Studying the gap between moment estimators to evaluate latent variable models

### 2021-01-30 Draft.tex
Implemented Frob and pimped out draft

\title{Moment matching in latent variable model}

@@

\section{Probability identities}

@@

@@

\subsection{Moment matching for diagnostic}

For latent variable with a define forward mechanism, such as pPCA, GMM, HMM and VAE we can assess the ability of the forward model to capture the moment of the observation by comparing the DE with the FME.

>>>>

\title{Studying the gap between moment estimators to evaluate latent variable models}

@@

\section{Latent variable models}

\section{Moment estimators}

\subsection{Second moment}

@@

\subsection{First moment}

@@

\section{Gap between moment estimators}

For latent variable with a define forward mechanism, such as pPCA, GMM, HMM and VAE we can assess the ability of the forward model to capture the moment of the observation by comparing the DE with the FME. From now we refer to the object we are studying as MEGA (Moment Estimators GAp).

\subsection{Selecting a matrix norm}

Finally, in order to map the MEGA to something tangible and comparable we propose using a matrix norm of the MEGA. There exist a wide range of possible candidate, let us introduce a few a justify our finale choice.

We want to use a norm that looks at the global properties of the matrix and fortunately Rigollet \cite{rigollet15} introduces multiple norms that do so.

\subsection{Implementation of the selected norms}

\section{Experiments and results}

\section{Training with moment estimator matching}

\section{Conclusion}
